---
title: "birthdays"
author: "Dr K"
date: "February 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Todays Notes
Today the class all filed in the day of the year they were born on. It is a number from 1 (Jan 1) to 365 (Dec 31) to contemplate whether any two shared a birthday.


```{r}
BDdata <- read.csv("classBdays.csv")
days<-na.omit(BDdata$BD)
print(sort(days))
```
##What if we had 30 people in the class?

Sampling in R is a tool we use all the time. There is two ways to doi it.
with replacement and the other way is without replacemeny.

```{r}
bdays=seq(1:365)
class30 = sample(bdays,size=30,replace = TRUE)
print(sort(class30))
```

The code we just ran will change every time. 

To get a definative answer we have to run this a lot of times and "keep track"

We build a loop that every time we get a new class we count if there is a match.

```{r}
numits=1000
class=30
ccnt=0
for (i in 1:numits) {
 class30 = sample(bdays,size=30,replace = TRUE)
 if(length(unique(class30)) != 30) ccnt=ccnt+1
}
pval=ccnt/numits
odds=pval/(1-pval)
print(pval)
print(odds)
  
```
